A Technique for Inter-Catalogue Recommendations

### 2014-06-10 paper2/paper.tex

\title{A Technique for Inter-Catalogue Recommendations}
\author{Bill Chickering and Jamie Irvine\\
CS 399 with Anand Rajaraman\\
Stanford University}
\renewcommand{\today}{June 12, 2014}
\maketitle

@@

We model this as a problem of connecting recommender systems between disjoint
catalogues. The goal is to construct good recommendations from products in one
catalogue to products in the other. These catalogues may be from competing
retailers who don't have access to each other's user data. Thus, to keep the
problem general, we do not assume that we have any private internal data.
Instead, we constrain ourselves to use only the product information and internal
recommendations that are posted publicly to all users.

@@

In this paper, we outline a technique that leverages the intra-catalogue
recommendations of each catalogue to construct inter-catalgoue recommendations
between them. We focus on the clothing retailers, since they tend to all have
public recommendations for each product. Specifically, the data used for this
project was all collected from the public product webpages for Macy's.

\section*{Data}
For this work, we utilize most of the product catalog of Macy's as presented at
www.macys.com. This catalog consists of numerous categories of mostly apparel,
each of which includes hundreds to thousands of items. We confine this study to
the 49 categories within the two main parent categories ``Men'' and ``Women''
that contain at least 200 items that are associated to multiple brands. In
total, this dataset consists of 66,071 items in 49 categories with some items
listed in multiple categories. For each item we record its description, all
categories within which it is listed, and its associated recommendations. By
{\em recommendations}, we are referring to the items---there are typically four
in the case of Macy's---that are displayed on a product's details page under the
heading ``Customers Also Shopped''. The presence of these recommendations
implicitly forms a directed graph over the product catalogue, in which the nodes
are the {\em products} or {\em items} and the edges are the {\em
recommendations}. These graphs play a central role in this study.

\section*{Experiments}
Our goal is to develop methods for connecting initially disconnected
recommendation graphs. That is, given two online retailers, each with a website
that displays items in their respective catalogue, where each item is
accompanied by several {\em recommended} items, we are presented with two
disconnected recommendation graphs. We would like to associate ``good''
recommendations for items in one catalogue with items in the other catalogue. In
this way, we are effectively introducing edges that connect the two
recommendation graphs. Formulating this inter-retailer recommendations problem
in terms of graphs offers insight in how to evaluate our recommendation choices
as well as how to choose ``good'' recommendations. Leveraging the graph
structure for evaluation is discussed in this section while exploiting the graph
for the purpose of making better recommendations is addressed in a subsequent
section.

@@

Precision, recall, and $F_1$ score are well-known metrics for evaluating
prediction algorithms.  Together, these metrics capture how effective one is at
guessing the items within a target set. Consider a typical Macy's category, for
example, Dresses, which contains about $3,500$ items. Randomly partitioning
results in two sets, each with about $1,750$ items. For each interset
recommendation, we must therefore choose two nodes, one from each of the two
sets. That is, we have $1,750 \times 1,750 > 3 \times 10^6$ choices. Choosing
the correct edges is a formidable challenge to say the least. It is therefore
worth asking: Are some prediction errors better or worse than others? The graph
nature of our problem reveals that the answer is yes. It is better to guess an
edge that connects two items that are separated by two edges in the original
graph than to connect two items that are separated by five edges. We therefore
introduce the notion of {\em 2-precision}, {\em 2-recall}, and {\em 2-}$F_1$ are
defined as

\begin{align}
\text{\em 2-precision} &= \left|\left\{(u,v) \in P | d_L(u,v) \leq 2
\right\}\right|
\\\text{\em 2-recall} &= \left|\left\{(u,v) \in L | d_P(u,v) \leq 2
\right\}\right|
\\\text{\em 2-}F_1 &= 2\cdot \frac{\text{\em 2-precision} \cdot \text{\em
2-recall}}{\text{\em 2-precision} + \text{\em 2-recall}}
\end{align}
where $P$ is the set of predicted edges, $L$ is the set of lost edges (i.e.
those in the cut resulting from the partition), and $d_L(u,v)$ is the distance
between nodes $u$ and $v$ in the original unpartitioned graph, and $d_P(u,v)$ is
the distance between nodes $u$ and $v$ in the new graph formed using the
predicted edges in $P$.

@@

The second mapping-related baseline is the Random Mapper Recommender. As the
name suggests, this recommender is identical to the LSI Recommender, except that
it uses a randomly generated linear transformation to map between concept
spaces. These two baselines represent (not strict) upper and lower bounds on how
well the concept mapping performs. The results shows how much of a bottleneck
this step is.

@@

\begin{center}
\begin{tabular}{ | l | c | c | c |}
\hline
Method & 2-Precision & 2-Recall & 2-F1 Score \\ \hline\hline
Random &&&\\ \hline
Simple Content-based &&&\\ \hline
Neighborhood Content-based &&&\\ \hline
One Model &&&\\ \hline
Popularity Baselines &&&\\ \hline
\hspace*{0.5cm} Map to most popular &&&\\ \hline
\hspace*{0.5cm} Random concept mapping &&&\\ \hline
LSI &&&\\ \hline
\hspace*{0.5cm} + Normalized concept mapping &&&\\ \hline
\hspace*{0.5cm} + Zero-mean SVD &&&\\ \hline
\hspace*{0.5cm} + Bigrams from descriptions &&&\\ \hline
\hspace*{0.5cm} + Discounted popularity from random walks &&&\\ \hline
\hspace*{0.5cm} + Popularity for finding nearest neighbors &&&\\ \hline
\hspace*{0.5cm} + Number of recommendations based on popularity &&&\\ \hline

>>>>

\title{A Technique for Inter-Catalogue Recommendations}
\author{Bill Chickering and Jamie Irvine\\
CS 399 with Anand Rajaraman\\
Stanford University}
\renewcommand{\today}{June 11, 2014}
\maketitle

@@

We model this as a problem of connecting recommender systems between disjoint
catalogues. The goal is to construct good recommendations from products in one
catalogue to products in the other. These catalogues may be from competing
retailers who don't have access to each other's user data. Thus, to keep the
problem general, we do not assume that we have any private data.
Instead, we constrain ourselves to use only the product information and internal
recommendations that are posted publicly to all users.

@@

In this paper, we outline a technique that leverages the intra-catalogue
recommendations of each catalogue to construct inter-catalgoue recommendations
between them. We focus on clothing retailers, since they tend to all have
public recommendations for each product. Specifically, the data used for this
project was all collected from the public product webpages for Macy's.

\section*{Data}
For this work, we utilize most of the product catalog of Macy's as presented at
www.macys.com. This catalog consists of numerous categories of mostly apparel,
each of which includes hundreds to thousands of items. We confine this study to
the 49 categories within the two main parent categories ``Men'' and ``Women''
that contain at least 200 items that are associated to multiple brands. In
total, this dataset consists of 66,071 items in 49 categories with some items
listed in multiple categories. For each item we record its description, all
categories within which it is listed, and its associated recommendations. By
{\em recommendations}, we are referring to the items---there are typically four
in the case of Macy's---that are displayed on a product's details page under the
heading ``Customers Also Shopped''. The presence of these recommendations
implicitly forms a directed graph over the product catalogue, in which the nodes
are the {\em products} or {\em items} and the edges are the {\em
recommendations}. We call these types of graphs {\em recommendation graphs} and they play a central role in this study.

\section*{Experiments}
Our goal is to develop methods for connecting initially disconnected
recommendation graphs. Given two online retailers, each with a website
displaying their items along with several other {\em recommended} items from
their catalogue, we are presented with two disconnected recommendation graphs. 
We would like to associate ``good'' recommendations for items in one catalogue 
with items in the other catalogue. In this way, we are effectively introducing 
edges that connect the two recommendation graphs. Formulating this inter-retailer
recommendations problem in terms of graphs offers insight in how to evaluate our 
recommendation choices as well as how to choose ``good'' recommendations. 
Leveraging the graph structure for evaluation is discussed in this section while 
exploiting the graph for the purpose of making better recommendations is addressed 
in a subsequent section.

@@

Precision, recall, and $F_1$ score are well-known metrics for evaluating
prediction algorithms.  Together, these metrics capture how effective one is at
guessing items within a target set. Consider a typical Macy's category, for
example, Dresses, which contains approximately $3,500$ items. Randomly 
partitioning results in two sets, each with about $1,750$ items. For each 
interset recommendation, we must therefore choose two nodes, one from each of the two
sets. That is, we have $1,750 \times 1,750 > 3 \times 10^6$ choices. Choosing
the correct edges is a formidable challenge to say the least. It is therefore
worth asking: Are some prediction errors better or worse than others? The graph
nature of our problem reveals that the answer is yes. It is better to guess an
edge that connects two items that are separated by two edges in the original
graph than to connect two items that are separated by five edges. We therefore
introduce the notion of {\em 2-precision}, {\em 2-recall}, and {\em 2-}$F_1$ are
defined as

\begin{align}
\text{\em 2-precision} &= \left|\left\{(u,v) \in P | d_L(u,v) \leq 2
\right\}\right|
\\\text{\em 2-recall} &= \left|\left\{(u,v) \in L | d_P(u,v) \leq 2
\right\}\right|
\\\text{\em 2-}F_1 &= 2\cdot \frac{\text{\em 2-precision} \cdot \text{\em
2-recall}}{\text{\em 2-precision} + \text{\em 2-recall}}
\end{align}
where $P$ is the set of predicted edges, $L$ is the set of lost edges (i.e.
those in the cut resulting from the partition), $d_L(u,v)$ is the shortest
distance between nodes $u$ and $v$ in the original unpartitioned graph, and 
$d_P(u,v)$ is the shortest distance between nodes $u$ and $v$ in the new graph 
formed using the predicted edges in $P$.

@@

The second mapping-related baseline is the Random Mapper Recommender. As the
name suggests, this recommender is identical to the LSI Recommender, except that
it uses a randomly generated linear transformation to map between concept
spaces. These two baselines represent (not strict) upper and lower bounds on how
well the concept mapping performs. The results show how much of a bottleneck
this step is.

@@

\begin{center}
\begin{tabular}{ | l | c | c | c |}
\hline
Method & 2-Precision & 2-Recall & 2-F1 Score \\ \hline\hline
Random &&&\\ \hline
Simple Content-based &&&\\ \hline
Neighborhood Content-based &&&\\ \hline
One Model &&&\\ \hline
Random concept mapping &&&\\ \hline
Popularity &&&\\ \hline
LSI &&&\\ \hline
\hspace*{0.5cm} + Normalized concept mapping &&&\\ \hline
\hspace*{0.5cm} + Zero-mean SVD &&&\\ \hline
\hspace*{0.5cm} + Bigrams from descriptions &&&\\ \hline
\hspace*{0.5cm} + Discounted popularity from random walks &&&\\ \hline
\hspace*{0.5cm} + Popularity for finding nearest neighbors &&&\\ \hline
\hspace*{0.5cm} + Number of recommendations based on popularity &&&\\ \hline
